High Resolution Spectroscopic Analysis of Orphan Stream Giants

### 2012-07-24 2012-oss/draft-oss.tex
updated

\begin{deluxetable*}{lcccccc}
\tablecolumns{2}
\tabletypesize{\scriptsize}
\tablecaption{Observed Targets\label{tab:observed-targets}}
\tablehead{
	\colhead{Star} &
	\colhead{$\alpha$} &
	\colhead{$\delta$} &
	\colhead{Air mass} &
	\colhead{S/N\tablenotemark{a}} &
	\colhead{$V_{\mbox{helio}}$} &
	\colhead{Comment} \\
 & (J2000) & (J2000) & & (px$^{-1}$) & (km s$^{-1}$) &
}
\startdata
HD 136316 & 15 22 17.2 & $-$53 14 13.9 & 1.118 & 335 & $-38.21 \pm 1.09$ & \\
HD 141531 & 15 49 16.9 & 09 36 42.5 & 1.309 & 280 & $2.63 \pm 1.02$ & \\
HD 142948 & 16 00 01.6 & $-$53 51 04.1 & 1.107 & 271 & $30.26 \pm 0.87$ & \\
HD 41667 & 06 05 03.7 & $-$32 59 36.8 & 1.005 & 272 & $297.79 \pm 1.72$ & \\
HD 44007 & 06 18 48.6 & $-$14 50 44.2 & 1.033 & 239 & $163.41 \pm 1.25$ & \\
HD 47536 & 06 37 47.7 & $-$32 20 20.1 & 1.002 & 257 & $78.87 \pm 1.21$ & \\
HD 76932 & 08 58 44.2 & $-$16 07 54.2 & 1.158 & 289 & $119.18 \pm 1.18$ & \\
HD 84903 & 09 47 19.3 & $-$41 27 04.9 & 1.260 & 294 & $77.65 \pm 1.41$ & \\
HD 59984 & 07 32 05.7 & $-$08 52 56.1 & 1.111 & 402 & $55.74 \pm 0.53$ & \\
HD 60060 & 07 29 59.6 & $-$52 39 04.3 & 1.127 & 414 & $25.60 \pm 1.08$ & \\
HD 60228 & 07 30 30.8 & $-$54 23 58.6 & 1.139 & 338 & $48.58 \pm 1.67$ & \\
OSS TGT 1    & 10 46 50.6 & $-$00 13 17.9 & 1.363 & 48 & $218.15 \pm 1.72$ & \\
OSS TGT 2    & 10 47 17.8 &    00 25 06.9 & 1.995 & 59 & $222.16 \pm 1.28$ & \\
OSS TGT 3    & 10 47 30.3 & $-$00 01 22.6 & 1.156 & 49 & $226.35 \pm 1.27$ & \\
OSS TGT 4    & 10 49 08.3 &    00 01 59.3 & 1.881 & 48 & $227.50 \pm 2.05$ & Poor seeing.\\
OSS TGT 5    & 10 50 33.7 &    00 12 18.3 & 1.295 & 31 & $249.01 \pm 2.58$ & Poor seeing. \\
HR 6141  & 16 30 12.3 & $-$25 06 52.0 & 1.003 & 406 & - & Telluric std.

@@

\subsection{Telluric Absorption Correction}

We observed the spectroscopic white dwarf HR6141 on March 15th, 2011 with the same slit configuration. The airmass during during this observation was 1.003. We assume all detected absorption lines in this spectrum are atmospheric, except for H$\alpha$. Continuum and absorption features in each echelle order were identified by eye and the spectrum was normalised using cubic splines with defined knot spacings. Overlapping echelle orders were stitched together and the normalised telluric template was interpolated onto the wavelength array for our observed stars. Each stellar spectrum was corrected by the normalised template adjusted by the ratio of the air masses, following the Beer-Lambert law:

\begin{equation}
d = \frac{s}{t^{X_{(obs)}/X_{(tel)}}}
\end{equation}

\subsection{Radial Velocities}
We measured radial velocities for every target by cross-correlating each telluric-divided observed spectrum with a synthetic template of $T_{eff} = 4500$ K, $\log{g} = 2.5$, [Fe/H] = -1.5, and [$\alpha$/Fe] = 0.0 over the wavelength region $845$ nm $< \Lambda < 870$ nm. Observed spectra were shifted to rest frame for line measurements. A number of radial velocity and halo standards were observed during this program, and our heliocentric velocities agree excellently with literature values.

@@

>>>>

\subsection{Observations}

\begin{deluxetable*}{lcccccc}
\tablecolumns{2}
\tabletypesize{\scriptsize}
\tablecaption{Observed Targets\label{tab:observed-targets}}
\tablehead{
	\colhead{Star} &
	\colhead{$\alpha$} &
	\colhead{$\delta$} &
	\colhead{Air mass} &
	\colhead{Seeing} &
	\colhead{S/N\tablenotemark{a}} &
	\colhead{$V_{\mbox{helio}}$} &
	\colhead{Comment} \\
 & (J2000) & (J2000) & & (") & (px$^{-1}$) & (km s$^{-1}$) &
}
\startdata
HD 136316 & 15 22 17.2 & $-$53 14 13.9 & ? & 1.118 & 335 & $-38.21 \pm 1.09$ & \\
HD 141531 & 15 49 16.9 & 09 36 42.5 & ? & 1.309 & 280 & $2.63 \pm 1.02$ & \\
HD 142948 & 16 00 01.6 & $-$53 51 04.1 & ? & 1.107 & 271 & $30.26 \pm 0.87$ & \\
HD 41667 & 06 05 03.7 & $-$32 59 36.8 & ? & 1.005 & 272 & $297.79 \pm 1.72$ & \\
HD 44007 & 06 18 48.6 & $-$14 50 44.2 & ? & 1.033 & 239 & $163.41 \pm 1.25$ & \\
HD 47536 & 06 37 47.7 & $-$32 20 20.1 & ? & 1.002 & 257 & $78.87 \pm 1.21$ & \\
HD 76932 & 08 58 44.2 & $-$16 07 54.2 & ? & 1.158 & 289 & $119.18 \pm 1.18$ & \\
HD 84903 & 09 47 19.3 & $-$41 27 04.9 & ? & 1.260 & 294 & $77.65 \pm 1.41$ & \\
HD 59984 & 07 32 05.7 & $-$08 52 56.1 & ? & 1.111 & 402 & $55.74 \pm 0.53$ & \\
HD 60060 & 07 29 59.6 & $-$52 39 04.3 & ? & 1.127 & 414 & $25.60 \pm 1.08$ & \\
HD 60228 & 07 30 30.8 & $-$54 23 58.6 & ? & 1.139 & 338 & $48.58 \pm 1.67$ & \\
OSS 1    & 10 46 50.6 & $-$00 13 17.9 & 0.8 & 1.363 & 48 & $218.15 \pm 1.72$ & \\
OSS 2    & 10 47 17.8 &    00 25 06.9 & ? & 1.995 & 59 & $222.16 \pm 1.28$ & \\
OSS 3    & 10 47 30.3 & $-$00 01 22.6 & 0.71 & 1.156 & 49 & $226.35 \pm 1.27$ & \\
OSS 4    & 10 49 08.3 &    00 01 59.3 & ? & 1.881 & 48 & $227.50 \pm 2.05$ & Poor seeing.\\
OSS 5    & 10 50 33.7 &    00 12 18.3 & ? & 1.295 & 31 & $249.01 \pm 2.58$ & Poor seeing. \\
HR 6141  & 16 30 12.3 & $-$25 06 52.0 & ? & 1.003 & 406 & - & Telluric std.

@@

\subsection{Data Reduction}
The data were reduced using the latest version of the MIKE pipeline outlined in \citet{Kelson;2003}. For comparison we also reduced our HD 59984 spectra using standard methods in \textsc{IRAF} and found no noteworthy difference between the reduced products. Individual frames for each object were co-added before analysis. We carefully normalised every echelle order using cubic splines. Overlapping normalised orders on each CCD were stitched together, such that a continuous normalised spectra from each CCD remains. We do not include line measurements that are susceptible to telluric absorption, so no telluric corrections were made.

\subsection{Radial Velocities}
We measured radial velocities for every target by cross-correlating each normalised red  spectrum with a synthetic template. Our synthetic template was generated in \textsc{MOOG}\footnotemark{a}\footnotetext{Sneden's website} using a \citet{Castelli-Kurucz;2004} model atmospheres with $T_{eff} = 4500$ K, $\log{g} = 2.5$, [Fe/H] = -1.5, [$\alpha$/Fe] = 0.0 and no convective overshoot. The line list of \citet{Kirby;et-al_2008} was employed to generate spectra between $845$ nm $< \Lambda < 870$ nm. Both the blue and red co-added, normalised frames were shifted to rest before equivalent width measurements. A number of radial velocity and halo standards were observed during this program, and our heliocentric velocities agree excellently with literature values (Table \ref{tab:observed-targets}).

@@

HD59984 5750 K, 1.55 vt, 3.55 logg -0.95,+0.40,
================================================
Fe I EPS 6.52 +/- 0.16 (210 lines)
Slope, Offset, Corr: 0.01, 6.53, 0.05

Fe I REW
Slope, Offset, Corr: 0.0, 6.55, 0.00

Fe I lambda
Slope, Offset, Corr: 3.84e-05, 6.35, 0.17

Fe II EPS 6.53 +/- 0.18 (22 lines)

Fe II REW
Slope, Offset, Corr: 0.07, 6.94, 0.09

Fe II lambda
Slope, Offset, Corr: 1.41e-04, 5.91, 0.36

OSS 2: JMK = 0.633
4571.9947676752899 K using Alonso 1999 paper
inspected all profiles + saved only Fe ones that were good in red + blue
================================================
4600 K, 1.85, 0.80, -1.77, 0.40

Fe I: 5.73 +/- 0.14 (139 lines)

Fe I EPS
S, O, C: 0.00, 5.72, 0.01

Fe I REW
S, O, C: -0.03, 5.58, -0.04

Fe I Lambda:
S, O, C: 3.98e-05, 5.51, 0.21

Fe II: 5.72 +/- 0.16 (21 lines)

Fe II EPS: None

Fe II REW S, O, C: 0.03, 5.84, 0.05

Fe II Lambda: 2.1e-05, 5.58, 0.09
